Estimating Correspondences of Deformable Objects ``In-the-wild"

### 2015-11-06 contents/evaluation.tex
Updates from ShareLaTeX

This sections evaluates the performance of proposed methodology in estimating correspondences of human poses in-the-wild. Results for quantitative an qualitative experiments are reported. Experiments \ref{exp:daam_benchmark} show performance of fitting dense SDMs built to non-rigid objects having rich interior textures e.g. faces and ears. Experiments \ref{exp:benchmark} compare the joints localisation accuracy of our skeleton prediction from outline fitting with respect to that of state-of-the-art human pose estimation algorithms in-the-wild. In addition, this experiment investigates the impact of annotating outlines of human poses instead of annotating skeletons. Note that all results reported in this section were obtained by fitting patch-based AAM using the fast version of the Simultaneous Inverse Compositional algorithm (Fast-SIC) originally proposed by the authors of \cite{Papandreou2008}. For further experimental results and visualisations please refer to our supplementary material.

@@

This experiment compares the fitting accuracy of our dense Active Appearance Models (dAAMs) versus the one of classic AAM on the problem of nonrigid face and ear alignment in-the-wild.

@@

>>>>

We evaluate the performance of the proposed methodology in experiments of estimating correspondences of human poses in-the-wild and in non-rigid object alignment in-the-wild.  For further experimental results and visualisations please refer to our supplementary material.

%Results of quantitative and qualitative evaluations are reported.

@@

This experiment compares the fitting accuracy of dense Active Appearance Models (dAAMs) trained with the proposed framework, as compared to classic AAMs. We here consider two object classes that have rich interior textures: faces and ears. The comparisons are for the problem of non-rigid face and ear alignment in-the-wild.

@@

Experiments \ref{exp:benchmark} compare joints localisation accuracy of our skeleton prediction from outline fitting with respect to that of state-of-the-art human pose estimation algorithms in-the-wild. In addition, the experiment investigates the impact of annotating outlines of human poses instead of annotating skeletons. Note that all results reported in this section were obtained by fitting patch-based AAM using the fast version of the Simultaneous Inverse Compositional algorithm (Fast-SIC) originally proposed by the authors of \cite{Papandreou2008}.

### 2015-11-06 contents/implementation.tex
Updates from ShareLaTeX

Using the constructed correspondence basis, the shape flow can be approximated as:
\begin{equation}\label{eq:LinTrajModel}
    \bm{u}_n(\bx) \approx
    \sum_{i=1}^R\bm{q}_i(n)\bm{v}_i(\bx) \,\, ,
\end{equation}
where $\bm{v}_i(\bx)$ is the weight that needs to be applied on the $i$-th correspondence basis element, in order to get the correspondence vector for the point location $\bm{x}$. In other words, the shape flow for every point $\bm{x}$ is described as a linear combination of basis elements that is controlled by the coefficients $\bm{v}_i(\bm{x})$.
The values of the $i$-th coefficient for all the points $\bm{v}_i(\bm{x})$ can be interpreted as an image defined on $\Omega$. Using the correspondence basis, the determination of the shape flow boils down to the determination of the set of coefficients $\bm{v}_i(\bm{x})$. The above representation of shape flow, constrains the correspondence vectors to lie on a subspace and, therefore, acts as a low-rank prior that enforces coherency of the shape registration result over the whole training dataset of shapes.

@@

\paragraph{Dense Active Appearance Model} Since all the deformation fields acquired by Step~\ref{sec:step3} contain the same number of pixels, which are the same as in the reference frame, the spatial positions $\bm{x}_i=(x_i, y_i)$ of these pixels can be treated as point landmarks and the deformation fields as dense annotations of the object's shape. Consequently, building a dense shape model reduces to normalising these dense annotations with respect to a global similarity transform (typically using Procrustes Analysis) and applying PCA. A shape instance can be generated by the resulting shape model as:
\begin{equation}
    \bm{s}(\bm{p}) = \bm{\bar{s}} + \bm{S} \bm{p}
    \label{eq:shape_model}
\end{equation}
where $\bm{\bar{s}}$ is mean shape, and $\bm{S}$ and $\bm{p}$ are the shape bases and shape parameters, respectively.

>>>>

Using the constructed correspondence basis, the shape flow can be approximated as:
\begin{equation}\label{eq:LinTrajModel}
    \bm{u}_n(\bx) \approx
    \textstyle \, \sum_{i=1}^R \, \bm{q}_i(n)\bm{v}_i(\bx) \,\, ,
\end{equation}
where $\bm{v}_i(\bx)$ is the weight that needs to be applied on the $i$-th correspondence basis element, in order to get the correspondence vector for the point location $\bm{x}$. In other words, the shape flow for every point $\bm{x}$ is described as a linear combination of basis elements that is controlled by the coefficients $\bm{v}_i(\bm{x})$.
The values of the $i$-th coefficient for all the points $\bm{v}_i(\bm{x})$ can be interpreted as an image defined on $\Omega$. Using the correspondence basis, the determination of the shape flow boils down to the determination of the set of coefficients $\bm{v}_i(\bm{x})$. The above representation of shape flow, constrains the correspondence vectors to lie on a subspace and, therefore, acts as a low-rank prior that enforces coherency of the shape registration result over the whole training dataset of shapes.

@@

\paragraph{Dense Active Appearance Model} Since all the deformation fields acquired by Step~\ref{sec:step3} are defined for the pixels of the reference SVS image, the spatial positions $\bm{x}_i=(x_i, y_i)$ of these pixels can be treated as point landmarks and the deformation fields as dense annotations of the object's shape. Consequently, building a dense shape model reduces to normalising these dense annotations with respect to a global similarity transform (typically using Procrustes Analysis) and applying PCA. A shape instance can be generated by the resulting shape model as:
\begin{equation}
    \bm{s}(\bm{p}) = \bm{\bar{s}} + \bm{S} \bm{p}
    \label{eq:shape_model}
\end{equation}
where $\bm{\bar{s}}$ is mean shape, and $\bm{S}$ and $\bm{p}$ are the shape bases and shape parameters, respectively.
